Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-16 blind.tex
Sync submitted version onto GitHub

\section{Achieving Blindness on $\QPIP_0$ protocols}
\label{sec:BlindBQP2}

@@

To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol. For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$. Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol. Finally, for the issue of the prover sending invalid ciphertext, we can assume without loss of generality that the decryption

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ corresponding to $\Pi_0$}
    Inputs:
    \begin{itemize}
        \item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
        \item Verifier's input: $x\in\zo^n$
    \end{itemize}

>>>>

\section{Generic Blindness Protocol Compiler for $\QPIP_0$}
\label{sec:BlindBQP2}

@@

To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol. For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$. Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol. Finally, for the issue of the prover sending invalid ciphertexts, we note that this is not an issue if the decryption never fails, which can be achieved by simply let the decryption algorithm output a default dummy message (e.g., $0$) when it fails.

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ corresponding to $\Pi_0$}
    Inputs:
    \begin{itemize}
        \item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
        \item Verifier's input: $x\in\zo^{\poly(\lambda)}$
    \end{itemize}

### 2020-04-16 introduction.tex
Sync with local to fix smart quotes
Sync submitted version onto GitHub

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations.
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers.
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
We refer curious readers to the survey~\cite{survey:GKK19} for details.

@@

However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$.
One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols.
However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
We end up developing a weaker version of parallel repetition result of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
More intuitions and detailed analysis are given in \Cref{sec:qpip0_all}.

>>>>

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier/client (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations.
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,FK17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non-communicating quantum provers.
In a recent breakthrough, Mahadev~\cite{FOCS:Mahadev18a} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines.
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}).
We refer curious readers to the survey~\cite{survey:GKK19} for details.

@@

However, we cannot directly make use of these parallel repetition results due to the subtle difference between protocols for $\BQP$ and $\SampBQP$.
One of the major difficulties here is still to deal with both the test part and the output part in $\SampBQP$ protocols.
However, because we are now in the computational setting, there is no longer any available quantum de Finetti theorem that is usually derived in the information-theoretic setting.
We end up developing a weaker version of  parallel repetition of Mahadev's protocol inspired by the technique from~\cite{arXiv:ChiaChungYam19}.
Due to the nature of parallel repetition in the computational setting, our analysis is much less modular and significantly involved for this part.  
More intuitions and detailed analysis are given in \Cref{sec:qpip0_all}.

### 2020-04-16 qpip0.tex
Sync submitted version onto GitHub

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
    Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
    Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
    then the verifier's output in the Hadamard round is $(\eps+\negl(\lambda))$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}
\begin{proof}
    Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.

@@

    Observe that this $\Pstar$ passes testing round with overwhelming probability by construction,
    so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
    That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.
    Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
    we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is computationally indistinguishable to $(d', z_{ideal}')$.

    Now we relate $(d', z')$ back to $(d, z)$.
    Conditioned on $\PNaiveStar$ accept, clearly $(d, z)=(d', z')$.
    Conditioned on $\PNaiveStar$ reject, since dummy strategy will be rejected with high probability in Hadamard round, %\Ethan{kinda obvious but we never explicitly explained why}
    we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$.
    So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,
    which in turn implies $\abs{d-d'}\leq O(\eps)$
    and $(d, z_{ideal})\approx_{c, O(\eps)}(d', z_{ideal}')$.
    Combining everything, we conclude that $(d, z)\approx_{c, O(\eps)}(d, z_{ideal})$.
\end{proof}

>>>>

\begin{lemma}[binding property of $\PiNaive$]
\label{lem:naive-qpip0-binding}
    Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
    Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting, $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
    then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
\end{lemma}
\begin{proof}
    Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.

@@

    Observe that this $\Pstar$ passes testing round with overwhelming probability by construction,
    so we can apply \Cref{lem:urmila-binding} to the $\PiMeasure$ call to use its binding property (\Cref{lem:urmila-binding}).
    That is, there exists some $\rho$ such that $v=M_{XZ}(\rho, h)$.
    Combining it with $\PiSamp$'s soundness (\Cref{QPIP1thm}),
    we see that $(d', z')\leftarrow(\Pstar, \VNaive)(1^\lambda, 1^{1/\varepsilon}, x)$ is $\eps$-computationally indistinguishable to $(d', z_{ideal}')$.

    Now we relate $(d', z')$ back to $(d, z)$.
    First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with high probability in Hadamard round,
    we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$ conditioned on $\PNaiveStar$ aborts.
    For the other case, conditioned on $\PNaiveStar$ not aborts, clearly $(d, z)=(d', z')$.
    So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,
    which in turn implies $\abs{d-d'}\leq O(\eps)$
    and $(d, z_{ideal})\approx_{c, O(\eps)}(d', z_{ideal}')$.
    Combining everything, we conclude that $(d, z)\approx_{c, O(\eps)}(d, z_{ideal})$.
\end{proof}
